---
title: "Final Project"
author: "Rohit Kumar & Channing Vernon"
date: "11/12/2019"
output:
  pdf_document: default
  html_document: default
---



```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
require("knitr")
opts_knit$set(root.dir = "C:/Users/William Roche/Documents/GitHub/Git2/S-P500Trends/sandp500")
#Need to make this a relative path so anyone can load the dataset easily

library(tidyverse)
library(dplyr)
#Loading all necessary libraries

```

# Installing required packages and Libraries

```{r}
library(tidyverse)
library(dplyr)
```



<br>

# Loading Data + Cleaning
```{r}
## Goals:
# Cleaning up data, making it easier to read. 
# **ALso need to filter out any NA's.**

data <- read.csv("all_stocks_5yr.csv")

summary(data)
str(data)

SP_data <- data %>%
  select(Name,date,open,low,high,close, volume)
# Changing the order of the columns

```


**Ommiting `NA` rows vs replacing them with `0`**
```{r}
SP_data <- na.omit(SP_data)
#SP_data[is.na(SP_data)] <- 0

# Omitting rows with NA values in order to make calculations error free, vs setting them to 0.

summary(SP_data)
```

<br>
# Changing date column from a factor to date
```{r}
# Making the "date" column usable.

SP_data$Date <- as.Date(SP_data$date, format = "%Y-%m-%d")
SP_data$date <- NULL
# Changing the date column format into a new variable, and deleting the previous one

summary(SP_data)

```

```{r, message = FALSE, include = TRUE, eval = FALSE}
## Goals
# Figuring out how to categorize the data into 500 indiviual companies, manually or via
# automation/funtion.

SP_data %>%
  group_by(Name) %>%
  select(Name) %>%
  unique()
#summary(SP_data)
```


#Top S&P 500 Stocks 

* S&P500 Sectors
- Information Technology
- Health Care
- Financials
- Communications Services
- Industrials
- Consumer Staples
- Energy
- Utilities
- Real Estate
- Materials
- 
- 
- 
- 
- 
- 




<br>
**Information Technology - 19.9%**

* CRM
* MFST
* CSCO
* V
* INTC

`https://us.spindices.com/indices/equity/sp-500-information-technology-sector`




```{r, message = FALSE, warning = FALSE}
SP_InfoTech <- ggplot(SP_data %>% filter(Name %in% c("CRM", "MSFT", "CSCO", "V", "INTC")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Top InfoTech Stocks", subtitle = "2013 to 2018", y = "Date", x = "Closing price (USD)") + facet_wrap(~Name)
  
SP_InfoTech
```

<br>

**Health Care - 15.8%**

* JNJ
* UNH
* MRK
* ABT
* LLY

`https://us.spindices.com/indices/equity/sp-500-health-care-sector`



```{r, message = FALSE, warning = FALSE}
SP_HealthCare <- ggplot(SP_data %>% filter(Name %in% c("JNJ", "UNH", "MRK", "ABT", "LLY")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Top HealthCare Stocks", subtitle = "2013 to 2018", y = "Date", x = "Closing price (USD)") + facet_wrap(~Name)
  
SP_HealthCare
```

<br>

**Financials - 13.7%**

* BRK.B
* JPM
* BAC
* WFC
* C

`https://us.spindices.com/indices/equity/sp-500-financials-sector`

```{r, message = FALSE, warning = FALSE}
SP_Financials <- ggplot(SP_data %>% filter(Name %in% c("BRK.B", "JPM", "BAC", "WFC", "C")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Top Financials Stocks", subtitle = "2013 to 2018", y = "Date", x = "Closing price (USD)") + facet_wrap(~Name)
  
SP_Financials
```

<br>

**Consumer Discretionary - 9.9%**
* AMZN
* HD
* MCD
* NKE
* SBUX

`https://us.spindices.com/indices/equity/sp-500-consumer-discretionary-sector`


```{r, message = FALSE, warning = FALSE}
SP_ConsumerDisc <- ggplot(SP_data %>% filter(Name %in% c("HD", "MCD", "NKE", "SBUX")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Top Consumer Discretionary Stocks", subtitle = "2013 to 2018", y = "Date", x = "Closing price (USD)") + facet_wrap(~Name)
  
SP_ConsumerDisc
```

```{r}
"AMZN"
```


<br>

**Communications Services - 9.9%**

* Facebook
* Alphabet Inc. Class A and Class C (GOOG & GOOGL)
* Charter Communications Inc Class A
* Walt Disney
* NFLX, AT&T, Verizon, comcast, activision

`https://us.spdrs.com/en/etf/the-communication-services-select-sector-spdr-fund-XLC`


```{r, message = FALSE, warning = FALSE}
SP_CommServices <- ggplot(SP_data %>% filter(Name %in% c("FB", "GOOGL", "CHTR", "DIS", "NFLX")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Top Communication Services Stocks", subtitle = "2013 to 2018", y = "Date", x = "Closing price (USD)") + facet_wrap(~Name)
  
SP_CommServices
```

<br>

**Industrials - 9.4%**

* BA
* HON
* UNP
* UTX
* MMM, LMT, GE

`https://us.spindices.com/indices/equity/sp-500-industrials-sector`


```{r, message = FALSE, warning = FALSE}
SP_Industrials <- ggplot(SP_data %>% filter(Name %in% c("BA", "HON", "UNP", "UTX", "MMM")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Top Industrials Stocks", subtitle = "2013 to 2018", y = "Date", x = "Closing price (USD)") + facet_wrap(~Name)
  
SP_Industrials
```


```{r, message = FALSE, warning = FALSE}
SP_ConsumerStaples <- ggplot(SP_data %>% filter(Name %in% c("PM", "PEP", "KO", "PG", "WMT")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Top Consumer Staples Stocks", subtitle = "2013 to 2018", y = "Date", x = "Closing price (USD)") + facet_wrap(~Name)
  
SP_ConsumerStaples
```

<br>

**Energy - 5.4%**

* XOM
* RDS.A (shell) *Not in the s&p 500 b/c it is not considered in the US market*
* CVX
* TOT
* BP, PTR, NEE

`https://www.fool.com/investing/the-10-biggest-energy-stocks.aspx`

&

`https://www.fool.com/investing/2018/09/06/the-5-biggest-oil-stocks-in-the-us.aspx`


```{r, message = FALSE, warning = FALSE}
SP_Energy <- ggplot(SP_data %>% filter(Name %in% c("EOG", "COP", "NEE", "XOM", "CVX")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Top Energy Stocks", subtitle = "2013 to 2018", y = "Date", x = "Closing price (USD)") + facet_wrap(~Name)
  
SP_Energy
```

<br>

**Utilities - 3.1%**

* PPL
* D
* SO
* DUK
* CNNP, AES, EIX, FE, ED

`https://www.barrons.com/articles/you-may-be-surprised-which-stock-market-sector-has-been-the-hottest-in-the-past-year-51570273500`


```{r, message = FALSE, warning = FALSE}
SP_Utilities <- ggplot(SP_data %>% filter(Name %in% c("PPL", "D", "DUK", "SO", "AES")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Top Utilities Stocks", subtitle = "2013 to 2018", y = "Date", x = "Closing price (USD)") + facet_wrap(~Name)
  
SP_Utilities
```

<br>

**Real Estate - 2.9%**

* ENSG
* ROIC
* AMT
* VNO
* HST, CBRE, WELL, PLD, CCI

`https://www.fool.com/investing/2019/01/13/the-3-best-real-estate-stocks-to-buy-in-2019.aspx`

&

`https://www.investopedia.com/top-real-estate-stocks-4582128`


```{r, message = FALSE, warning = FALSE}
SP_RealEstate <- ggplot(SP_data %>% filter(Name %in% c("CCI", "PLD", "AMT", "VNO", "MAC")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Top Real Estate Stocks", subtitle = "2013 to 2018", y = "Date", x = "Closing price (USD)") + facet_wrap(~Name)
  
SP_RealEstate
```

<br>

**Materials - 2.6%**

* NUE
* LYB
* ALB
* NEM
* CF, FMC, 

`https://www.investopedia.com/top-materials-stocks-4582152`

```{r, message = FALSE, warning = FALSE}
SP_Materials <- ggplot(SP_data %>% filter(Name %in% c("NUE", "LYB", "ALB", "NEM", "CF")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Top Materials Stocks", subtitle = "2013 to 2018", y = "Date", x = "Closing price (USD)") + facet_wrap(~Name)
  
SP_Materials
```

<br>

```{r, message = FALSE, warning = FALSE, error = FALSE}

AMD_NVDA_INTC <- ggplot(filter(SP_data, Name %in% c("INTC", "AMD","NVDA")), aes(x = Date, y = close, color = Name)) + geom_point(alpha = 0, size = 1) + geom_smooth() + labs(title = "Intel vs AMD vs InVidia",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)") + theme_dark()

AMD_NVDA_INTC
```



<br>
```{r, messages = FALSE, warnings = FALSE}
AMD_NVDA_INTC_ <- ggplot(filter(SP_data, Name %in% c("INTC", "AMD","NVDA")), aes(x = Date, y = close, color = Name)) + geom_point() + labs(title = "Intel vs AMD vs InVidia",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)") + theme_dark()

AMD_NVDA_INTC_
```
# Questions


* 1. Which stock has the highest gains from 2013 - 2018?

```{r, warning=FALSE, message=FALSE}

SP_data %>%
 group_by(Name)%>%
 arrange(Name, Date) %>%
 filter(row_number()==1 | row_number()==n()) %>%
 mutate(gains = c(0,diff(close))) %>%
 filter(gains != "NULL" & gains!=0) %>%
 select(Name)

Start_Price <- SP_data %>%
  group_by(Name) %>%
  arrange(Name, Date) %>%
  filter(row_number()==1) %>%
  select(close)

End_Price <- SP_data %>%
  group_by(Name) %>%
  arrange(Name, Date) %>%
  filter(row_number()==n()) %>%
  select(close)
```


* 2. Which has the lowest?

* 3. Finding the p value with a t test and the null hypothesis.

* 4. Finding a way to implement the stocks with a confidence interval.

* 5. Compare the top companies.

* 6. Events that affected the stock market from 2013 - 2018.

* 7. Most popular stock?

* 8. Least popular stock?

* 9. T-test: Do energy stocks rise i nthe summer due to the fact that it is hotter than other months which would require more energy thus possibly raising energy stocks?































































