---
title: "Final Project"
author: "Rohit Kumar & Channing Vernon"
date: "11/12/2019"
output:
  pdf_document: default
  html_document: default
---



```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
require("knitr")
opts_knit$set(root.dir = "C:/Users/William Roche/Documents/GitHub/Git2/S-P500Trends/sandp500")
#Need to make this a relative path so anyone can load the dataset easily

library(tidyverse)
library(dplyr)
#Loading all necessary libraries

```

<br>

# Loading Data + Cleaning
```{r}
## Goals:
# Cleaning up data, making it easier to read. 
# **ALso need to filter out any NA's.**

data <- read.csv("all_stocks_5yr.csv")

summary(data)
str(data)

SP_data <- data %>%
  select(Name,date,open,low,high,close, volume)
# Changing the order of the columns

```


**Ommiting `NA` rows vs replacing them with `0`**
```{r}
SP_data <- na.omit(SP_data)
#SP_data[is.na(SP_data)] <- 0

# Omitting rows with NA values in order to make calculations error free, vs setting them to 0.

summary(SP_data)
```

<br>
# Changing date column from a factro to date
```{r}
# Making the "date" column usable.

SP_data$Date <- as.Date(SP_data$date, format = "%Y-%m-%d")
SP_data$date <- NULL
# Changing the date column format into a new variable, and deleting the previous one

summary(SP_data)

```

```{r, message = FALSE, include = FALSE, eval = FALSE}
## Goals
# Figuring out how to categorize the data into 500 indiviual companies, manually or via
# automation/funtion.

SP_data %>%
  group_by(Name) %>%
  select(Name) %>%
  unique()
# Listing all of the unique companies included in data set.

ABC <- ggplot(filter(SP_data, Name %in% c("ABC")), aes(x = Date, y = close)) + geom_point(alpha = (1/3), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "AmerisourceBergen Corp.",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)")

ABC

AAL <- ggplot(filter(SP_data, Name %in% c("AAL")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "American Airlines",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)")

AAL

AAL_ABC <- ggplot(filter(SP_data, Name %in% c("AAL","ABC")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "American Airlines & AmerisourceBergen Corp.",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)")

AAL_ABC






#summary(SP_data)
```


#Top S&P 500 Stocks 
* Categorized by competitors and similar industries
```{r, message = FALSE, include = FALSE, eval = FALSE}

AMD <- ggplot(filter(SP_data, Name %in% c("AMD")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Advanced Micro Devices",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)")

AMD


NVDA <- ggplot(filter(SP_data, Name %in% c("NVDA")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "InVidia",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)")

NVDA


INTC <- ggplot(filter(SP_data, Name %in% c("INTC")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Intel",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)")

INTC

```


```{r, include = FALSE, eval = FALSE, message = FALSE}

WMT <- ggplot(filter(SP_data, Name %in% c("WMT")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Walmart",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)")

WMT


AMZN <- ggplot(filter(SP_data, Name %in% c("AMZN")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Amazon",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)")

AMZN


MSFT <- ggplot(filter(SP_data, Name %in% c("MSFT")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Microsoft",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)")

MSFT


AAPL <- ggplot(filter(SP_data, Name %in% c("AAPL")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Apple",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)")

AAPL

```

```{r, include = FALSE, eval = FALSE}
TRIP <- ggplot(filter(SP_data, Name %in% c("TRIP")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Trip Advisor",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)")

TRIP


AAP <- ggplot(filter(SP_data, Name %in% c("AAP")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Advance Auto Parts",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)")

AAP



IBM <- ggplot(filter(SP_data, Name %in% c("IBM")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "IBM",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)")

IBM



RHT <- ggplot(filter(SP_data, Name %in% c("RHT")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Red Hat ",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)")

RHT

```


```{r, message = FALSE, warning = FALSE, include = FALSE, eval = FALSE}

MCD <- ggplot(filter(SP_data, Name %in% c("MCD")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Mcdonald's Corp.",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)")

MCD


CMG <- ggplot(filter(SP_data, Name %in% c("CMG")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Chipotle Mexican Grill",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)")

CMG


SBUX <- ggplot(filter(SP_data, Name %in% c("SBUX")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Starbucks",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)")

SBUX

#WEN <- ggplot(filter(SP_data, Name %in% c("WEN")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + #geom_smooth(lwd = 1, se = TRUE) + labs(title = "Wendy's Co",
#                        subtitle = "2013 to 2018",
#                        y = "Date",
#                        x = "Closing price (USD)")
#
#WEN

#KEYS <- ggplot(filter(SP_data, Name %in% c("KEYS")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = #2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Keysight Technologies Inc",
#                        subtitle = "2013 to 2018",
#                        y = "Date",
#                        x = "Closing price (USD)")
#
#KEYS


ORLY<- ggplot(filter(SP_data, Name %in% c("ORLY")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "O'Reilly Automotive",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)")

ORLY


FOX <- ggplot(filter(SP_data, Name %in% c("FOX")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Twentieth Century Fox",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)")

FOX


DIS <- ggplot(filter(SP_data, Name %in% c("DIS")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Disney",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)")

DIS

#HULU <- ggplot(filter(SP_data, Name %in% c("HULU")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = #2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "HULU",
#                        subtitle = "2013 to 2018",
#                        y = "Date",
#                        x = "Closing price (USD)")
#
#HULU


HCA <- ggplot(filter(SP_data, Name %in% c("HCA")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "HCA Healthcare",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)")

HCA


BSX <- ggplot(filter(SP_data, Name %in% c("BSX")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Boston Scientific",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)")

BSX


MKC <- ggplot(filter(SP_data, Name %in% c("MKC")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "McCormick & Co.",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)")

MKC


ILMN <- ggplot(filter(SP_data, Name %in% c("ILMN")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Ilumina Inc.",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)")

ILMN


NRG <- ggplot(filter(SP_data, Name %in% c("NRG")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "NRG Energy Co.",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)")

NRG


LLY <- ggplot(filter(SP_data, Name %in% c("LLY")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Eli Lilly & Co.",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)")

LLY


NFLX <- ggplot(filter(SP_data, Name %in% c("NFLX")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Netflix",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)")

NFLX


EW <- ggplot(filter(SP_data, Name %in% c("EW")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Edwards Lifesciences",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)")

EW


CRM <- ggplot(filter(SP_data, Name %in% c("CRM")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Salesforce.com",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)")

CRM


AES <- ggplot(filter(SP_data, Name %in% c("AES")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "AES Corporation",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)")

AES


RMD <- ggplot(filter(SP_data, Name %in% c("RMD")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "ResMed Inc.",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)")

RMD


CHD <- ggplot(filter(SP_data, Name %in% c("CHD")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Church & Dwight Co.",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)")

CHD


#LW <- ggplot(filter(SP_data, Name %in% c("LW")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + #geom_smooth(lwd = 1, se = TRUE) + labs(title = " Lamb Weston Holdings",
#                        subtitle = "2013 to 2018",
#                        y = "Date",
#                        x = "Closing price (USD)")
#
#LW


#VRNS <- ggplot(filter(SP_data, Name %in% c("VRNS")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Verisign",
#                        subtitle = "2013 to 2018",
#                        y = "Date",
#                        x = "Closing price (USD)")

#VRNS


BRK.B <- ggplot(filter(SP_data, Name %in% c("BRK.B")), aes(x = Date, y = close)) + geom_point(alpha = (1/6), size = 2) + geom_smooth(lwd = 1, se = TRUE) + labs(title = "Berkshire Hathaway Inc.(B)",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)")

BRK.B


```


# S&P500 Sectors


<br>
**Information Technology - 19.9%**

* AMD
* FTNT
* RHT
* KEYS
* MSI

`https://us.spindices.com/indices/equity/sp-500-health-care-sector`

<br>

**Health Care - 15.8%**

* JNJ
* UNH
* MRK
* ABT
* LLY

`https://us.spindices.com/indices/equity/sp-500-health-care-sector`

<br>

**Financials - 13.7%**

* BRK.B
* JPM
* BAC
* WFC
* C

`https://us.spindices.com/indices/equity/sp-500-financials-sector`

<br>

**Consumer Discretionary - 9.9%**

* AMZN
* HD
* MCD
* NKE
* SBUX

`https://us.spindices.com/indices/equity/sp-500-consumer-discretionary-sector`

<br>

**Communications Services - 9.9%**

* Facebook
* Alphabet Inc. Class A and Class C
* Charter Communications Inc Class A
* Walt Disney
* NFLX, AT&T, Verizon, comcast, activision

`https://us.spdrs.com/en/etf/the-communication-services-select-sector-spdr-fund-XLC`

<br>

**Industrials - 9.4%**

* BA
* HON
* UNP
* UTX
* MMM, LMT, GE

`https://us.spindices.com/indices/equity/sp-500-industrials-sector`

<br>

**Consumer Staples - 7.4%**

* WMT
* PG
* KO
* PEP
* PM, COST, MO

`https://www.fool.com/investing/the-10-biggest-consumer-staples-stocks.aspx`

<br>

**Energy - 5.4%**

* XOM
* RDS.A (shell)
* CVX
* TOT
* BP, PTR, NEE

`https://www.fool.com/investing/the-10-biggest-energy-stocks.aspx`

<br>

**Utilities - 3.1%**

* PPL
* D
* SO
* DUK
* CNNP, AES, EIX, FE, ED

`https://www.barrons.com/articles/you-may-be-surprised-which-stock-market-sector-has-been-the-hottest-in-the-past-year-51570273500`

<br>

**Real Estate - 2.9%**

* ENSG
* ROIC
* AMT
* VNO
* HST, CBRE, WELL, PLD, CCI

`https://www.fool.com/investing/2019/01/13/the-3-best-real-estate-stocks-to-buy-in-2019.aspx`

&

`https://www.investopedia.com/top-real-estate-stocks-4582128`

<br>

**Materials - 2.6%**

* NUE
* LYB
* ALB
* NEM
* CF, FMC, 

`https://www.investopedia.com/top-materials-stocks-4582152`


```{r, message = FALSE, warning = FALSE, error = FALSE}

AMD_NVDA_INTC <- ggplot(filter(SP_data, Name %in% c("INTC", "AMD","NVDA")), aes(x = Date, y = close, color = Name)) + geom_point(alpha = 0, size = 1) + geom_smooth() + labs(title = "Intel vs AMD vs InVidia",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)") + theme_dark()

AMD_NVDA_INTC
```



<br>
```{r, messages = FALSE, warnings = FALSE}
AMD_NVDA_INTC_ <- ggplot(filter(SP_data, Name %in% c("INTC", "AMD","NVDA")), aes(x = Date, y = close, color = Name)) + geom_point() + labs(title = "Intel vs AMD vs InVidia",
                        subtitle = "2013 to 2018",
                        y = "Date",
                        x = "Closing price (USD)") + theme_dark()

AMD_NVDA_INTC_
```





















